---
title: "p8105_hw6_zc2610"
author: "Zuoqiao Cui"
date: "2022-11-22"
output: github_document
---

```{r}
library(tidyverse)
library(modelr)
library(viridis)
library(mgcv)
```

# Problem 2

```{r}
homicide_data_df = read_csv("./data/homicide-data.csv") %>% 
janitor::clean_names()
```

Create a new variable "city_state" to combine city and state columns

```{r}
homicide_data_df = homicide_data_df %>% 
  mutate(
    city_state = str_c(city, state, sep = ",")
  ) %>% 
  select(-city,-state)
```

1. Create a new binary variable indicating whether the homicide is solved (0 means "unsolved" and 1 means "solved")

2. Omit cities Dallas, TX; Phoenix, AZ; Kansas City, MO and Tulsa, AL

3. Limit the analysis those for whom victim_race is white or black

4. Be sure victim_age is numeric

```{r}
homicide_data_df = homicide_data_df %>% 
  mutate(
    whether_solved = case_when(
      disposition == "Closed without arrest" ~ 0,
      disposition == "Open/No arrest" ~ 0,
      disposition == "Closed by arrest" ~ 1
    )
  ) %>% 
filter(
    city_state != "Dallas,TX" & city_state != "Phoenix,AZ" & city_state != "Kansas City,MO" & city_state != "Tulsa,AL"
  ) %>% 
    filter(victim_age != 'Unknown') %>% 
  mutate(victim_age = as.numeric(victim_age)) %>% 
  filter(victim_race == "White" | victim_race == "Black")
```

1. For the city of Baltimore, MD, use the glm function to fit a logistic regression with resolved vs unresolved as the outcome and victim age, sex and race as predictors 

2. Save the output of glm as an R object

3. Apply the broom::tidy to this object

```{r}
homicide_Baltimore_df = homicide_data_df %>% 
  filter(city_state == 'Baltimore,MD') 
Baltimore_glm = glm(whether_solved ~ victim_age + victim_sex + victim_race,data = homicide_Baltimore_df, family = binomial()) %>% 
  broom::tidy()
```

1. Obtain the estimate and confidence interval of the adjusted odds ratio for solving homicides

2. Compare male victims to female victims keeping all other variables fixed

```{r}
Baltimore_glm %>% 
  mutate(
    OR = exp(estimate),
    OR_lower = exp(estimate - std.error * 1.96),
    OR_upper = exp(estimate + std.error * 1.96)
        ) %>%
   select(term, log_OR = estimate, OR,OR_lower,OR_upper, p.value)

fit_logistic_sex = Baltimore_glm %>%
  filter(term == "victim_sexMale") %>% 
  mutate(
    OR = exp(estimate),
    OR_lower = exp(estimate - std.error * 1.96),
    OR_upper = exp(estimate + std.error * 1.96)
        ) %>%
   select(term, log_OR = estimate, OR,OR_lower,OR_upper, p.value)
```

Answer:

1. The estimate of the adjusted odds ratio for solving homicides comparing male victims to female victims is `r fit_logistic_sex$log_OR`

2. The confident interval is (`r fit_logistic_sex$OR_lower`,`r fit_logistic_sex$OR_upper`)



1. Run glm for each of the cities in the homicide dataset

2. Obtain regression results

3. Extract the adjusted odds ratio (and CI) for solving homicides

4. Compare male victims to female victims only

```{r}
fit_logistic_df = homicide_data_df %>% 
  select(victim_age,victim_race,victim_sex,city_state,whether_solved) %>% 
  nest(-city_state) %>% 
  mutate(
   models = map(.x = data, ~glm(whether_solved ~ victim_age + victim_sex + victim_race, family = binomial(link = logit), data = .x))
  ) %>% 
  mutate(
    results = map(models, broom::tidy)
  ) %>% 
  select(-data,-models) %>% 
  unnest(results) %>% 
   mutate(
    OR = exp(estimate),
    OR_lower = exp(estimate - std.error * 1.96),
    OR_upper = exp(estimate + std.error * 1.96)
        ) %>% 
  select(city_state,term,log_OR = estimate,OR,OR_lower,OR_upper)
fit_logistic_sex_df = fit_logistic_df %>% 
  filter(term == "victim_sexMale")
```

Create a plot that shows the estimated ORs and CIs for each city and organize cities according to estimated OR

```{r}
fit_logistic_sex_df %>% 
  mutate(city_state = fct_reorder(city_state, OR)) %>% 
  ggplot(aes(x = city_state, 
             y = OR, 
             ymin = OR_lower, 
             ymax = OR_upper,
             color = city_state
             )
  ) +
    geom_point() +
    geom_errorbar() +
    theme_bw() +
    labs(
      x = "City",
      y = "OR",
      title = "Odds ratios and CIs for solving homicides comparing gender",
      caption = "Homicide Data"
    ) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1, size = rel(0.8)),plot.title = element_text(hjust = 0.5),legend.position = "none") 
  
```

Comments:

1. New York, NY has the lowest odds ratio.

2. For cities whose OR is smaller than 1, males have lower odds compared to females. For cities whose OR is greater than 1, male has greater odds compared to female.


The confidence intervals of some cities (such as Chicago, JL) are narrow so that we can be more confident about future predictions for these cities.




# Problem 3

Import dataset

```{r}
birthweight_df = read_csv("./data/birthweight.csv") %>% 
janitor::clean_names()
```

Convert numeric to factor

```{r}
birthweight_df = birthweight_df %>% 
 mutate(
    babysex = as.factor(babysex),
    frace = as.factor(frace),
    malform = as.factor(malform),
    mrace = as.factor(mrace)
  )
```

Check missing data

```{r}
sum(!complete.cases(birthweight_df))
```

Answer:

There is no missing data in this dataset



